\cvsection{Experiences}

\begin{cventries}
  \cventry
  {Theia - National Healthtech Company} % Organization
  {Mid-level Back-end Developer} % Job title
  {São Paulo, SP (Remote)} % Location
  {Jun, 2022 - Present} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Developed} and \textbf{implemented} new services in \textbf{Go}, creating functionalities such as authentication, file uploads (\textbf{AWS S3}), and audit systems (\textbf{AWS SQS}).}
      \item {\textbf{Revamped} system architectures to better suit small team environments, \textbf{optimizing development workflows}.}
      \item {\textbf{Designed} and \textbf{expanded} the use of a common package among systems by consolidating an external library for greater \textbf{efficiency}.}
      \item {\textbf{Led} the development of the front-end and back-end interface, applying \textbf{best practices} for both user experience and developer interaction.}
      \item {\textbf{Implemented} traceability and metrics tools using \textbf{Prometheus} and \textbf{Grafana}, enhancing system visibility and monitoring.}
      \item {\textbf{Increased} test coverage of the main repositories by 50\%, utilizing tools such as \textbf{Testcontainers} for services like \textbf{AWS S3}, \textbf{SQS}, \textbf{DynamoDB}, and \textbf{PostgreSQL}.}
      \item {Languages: \textbf{GoLang}, \textbf{SQL}, \textbf{Kotlin}.}
      \item {Technologies: \textbf{AWS (S3, ECR, DynamoDB, SQS)}, \textbf{PostgreSQL}, \textbf{Chi}, \textbf{Testcontainers}, \textbf{GitHub}, \textbf{Swagger}, \textbf{JWT}, \textbf{OAuth 2.0}, \textbf{Prometheus}, \textbf{Grafana}.}
    \end{cvitems}
  }

  \cventry
  {Assert Laboratory - Scientific Research and Development Laboratory} % Organization/Project
  {Back-end Developer} % Job title
  {João Pessoa, PB (Remote)} % Location
  {Mar, 2024 - Mar, 2025} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Developed} REST APIs using \textbf{Django Rest Framework} for managing IoT devices and securely recording their data, applying \textbf{encryption} to protect communications between devices and the back-end.}
      \item {\textbf{Planned} and \textbf{implemented} the communication architecture between devices and systems, ensuring high efficiency and security in data flows.}
      \item {\textbf{Expanded} and \textbf{customized} the default Django user control API to meet the project’s specific requirements.}
      \item {\textbf{Implemented} a web system that displays real-time data from devices, including \textbf{alerts} configured based on the severity of data changes.}
      \item {\textbf{Documented} system endpoints using \textbf{OpenAPI (Swagger)}, improving traceability and integration with other developers.}
      \item {\textbf{Adopted} best development practices by following official documentation and \textbf{Django} community standards.}
      \item {Technologies: \textbf{Python}, \textbf{Django Rest Framework}, \textbf{PostgreSQL}, \textbf{Swagger (OpenAPI)}, \textbf{Encryption}, \textbf{WebSockets}.}
    \end{cvitems}
  }

  \cventry
  {Distributed Systems Laboratory (LSD) - Scientific Research and Development Laboratory} % Organization
  {Developer and Researcher} % Job title
  {Campina Grande, PB (Remote)} % Location
  {Aug, 2021 - Jun, 2022} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Conducted} research on information security solutions, developing technologies based on the virtualization of the \textbf{TPM 2.0} chip for the \textbf{VMware} platform.}
      \item {\textbf{Designed} and \textbf{implemented} solutions using \textbf{vTPM} to enhance the integrity and security of virtual machines, integrating the \textbf{VMware SDK} with \textbf{GoLang}.}
      \item {\textbf{Contributed} to the robustness and reliability of the virtual infrastructure by improving attack protection and ensuring greater compliance with security standards.}
      \item {Languages: \textbf{GoLang}, \textbf{Shell Script}.}
      \item {Technologies: \textbf{VMware}, \textbf{TPM 2.0}, \textbf{GNU/Linux}.}
    \end{cvitems}
  }

  \cventry
  {Resilia Educação - National EduTech Company} % Organization
  {Tech Facilitator} % Job title
  {Rio de Janeiro, RJ (Remote)} % Location
  {May, 2021 - Dec, 2021} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Facilitated} web development learning, assisting students in understanding key concepts and applying them in practical projects.}
      \item {\textbf{Taught} back-end development using \textbf{Express.js} and \textbf{JavaScript}, guiding students in creating APIs.}
      \item {\textbf{Advised} on database modeling by following best practices for data manipulation and organization in \textbf{MySQL}.}
      \item {\textbf{Instructed} on efficient \textbf{Docker} container management, streamlining workflows for beginner developers.}
      \item {Languages: \textbf{JavaScript}, \textbf{SQL}.}
      \item {Technologies: \textbf{Docker}, \textbf{Express.js}, \textbf{Node.js}, \textbf{MySQL}.}
    \end{cvitems}
  }

  \cventry
  {GCOMPI Laboratory - Scientific Research and Development Laboratory} % Organization
  {Research Scholar} % Job title
  {Campina Grande, PB} % Location
  {Jan, 2020 - May, 2021} % Date(s)
  {
    \begin{cvitems}
      \item {\textbf{Conducted} research in \textbf{Wireless Sensor Networks}, exploring new methods of communication and data collection.}
      \item {\textbf{Developed} firmware for the \textbf{OpenMote B} platform, enhancing radio communication with support for various modulations of the \textbf{IEEE 802.15.4g} protocol.}
      \item {\textbf{Analyzed} collected data using \textbf{Python}, directly contributing to the development of the final graduation project.}
      \item {Languages: \textbf{C++}, \textbf{Python}, \textbf{SQL-like}.}
      \item {Technologies: \textbf{InfluxDB}, \textbf{SCons}, \textbf{FreeRTOS}, \textbf{GNU/Linux}.}
    \end{cvitems}
  }
\end{cventries}
